Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass

### 2025-05-19 paper/paper_R1_natbib.Rmd
revised paper

---
title: "Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass"
author: 
  - Timothy J. Miller^1^
  - Kiersten L. Curti
  - Alexander C. Hansell
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: no
    number_sections: yes
    fig_caption: yes
    includes:
      in_header: options.sty
#    citation_package: biblatex
#biblio-style: authoryear
#  pdf_document:
#    keep_tex: yes
#    fig_caption: yes
#    number_sections: yes
#    includes:
#      in_header: options.sty
#  html_document:
#    df_print: paged
csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
bibliography: bsb-wham.bib
---

@@

# References {-}

>>>>

---
title: "Space for WHAM: a multi-region, multi-stock generalization of the Woods Hole Assessment Model with an application to black sea bass"
author: 
  - Timothy J. Miller^1^
  - Kiersten L. Curti
  - Alexander C. Hansell
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::pdf_document2:
    keep_tex: yes
    toc: no
    number_sections: yes
    fig_caption: yes
    citation_package: natbib
    includes:
      in_header: options.sty
#    citation_package: biblatex
#biblio-style: authoryear
#  pdf_document:
#    keep_tex: yes
#    fig_caption: yes
#    number_sections: yes
#    includes:
#      in_header: options.sty
#  html_document:
#    df_print: paged
# csl: canadian-journal-of-fisheries-and-aquatic-sciences.csl
natbiboptions: round
biblio-style: cjfas.bst
# bibliography: bsb-wham.bib
---

@@

\bibliography{bsb-wham}

### 2025-05-19 paper/symboltable_R1.tex
revised paper

$\delta_{s,j}$ & fraction of the annual time step between $t_s$ and the end of season $j-1$\\

@@

$\delta_{m,j}$ & fraction of the annual time step between $t_m$ and the end of season $j-1$\\

@@

$\text{SSB}_{s,y}$ & Spawning stock biomass for stock $s$ in year $y$\\

@@

$w_{s,y,a}$ & mean individual weight for stock $s$ at age $a$ in year $y$\\
$\text{mat}_{s,y,a}$ & proportion mature at age $a$ in year $y$ for stock $s$\\
$\mathbf{O}_{s,y,a,r_s}(t_s)$ & Probabilities of surviving and occurring in region $r_s$ at time $t_s$ given being alive in each region at the start of the year\\

@@

$\text{sel}_{1,a,f}$ & selectivity at age $a$ for fleet $f$ in the first year\\

@@

$\mathbf{O}_{a}$ & proportion surviving the year at age $j$ and occuring in each region (columns) given alive on January 1 in each region (rows)\\

@@

$\mu_{r\rightarrow r',y,a,i}$ & movement from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\
$g(\mu_{r\rightarrow r',y,a,i})$ & link function for movement $\mu_{r\rightarrow r',y,a,i}$\\
$\theta_{r\rightarrow r',i}$ & mean parameter across age and year for movement from region $r$ to region $r'$ in seasonal interval $i$\\
$\varepsilon_{r\rightarrow r',y,a,i}$ &  random effect parameter for movement from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\

@@

>>>>

$\delta_{s,i}$ & fraction of the annual time step between $t_s$ and the beginning of season $i$\\

@@

$\delta_{m,i}$ & fraction of the annual time step between $t_m$ and the beginning of season $i$\\

@@

$\text{SSB}_{y,r_s}$ & Spawning stock biomass for a given stock in region $r_s$ in year $y$\\

@@

$w_{y,a}$ & mean individual weight for a given stock at age $a$ in year $y$\\
$\text{mat}_{y,a}$ & proportion mature at age $a$ in year $y$ for a given stock\\
$\mathbf{O}_{y,a,r_s}(t_s)$ & Probabilities of surviving and occurring in region $r_s$ at time $t_s$ given being alive in each region at the start of the year\\

@@

$\text{sel}_{1,a,f}$ & selectivity scalar at age $a$ for fleet $f$ in the first year\\

@@

$\mathbf{O}_{a}$ & proportion surviving the year at age $a$ and occuring in each region (columns) given alive on January 1 in each region (rows)\\

@@

$\mu_{r\rightarrow r',y,a,i}$ & movement rate from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\
$g(\mu_{r\rightarrow r',y,a,i})$ & link function for movement rate $\mu_{r\rightarrow r',y,a,i}$\\
$\theta_{r\rightarrow r',i}$ & mean or intercept parameter across age and year for movement from region $r$ to region $r'$ in seasonal interval $i$\\
$\varepsilon_{r\rightarrow r',y,a,i}$ & random effect for movement from region $r$ to region $r'$ in seasonal interval $i$ and year $y$ at age $a$\\

@@

$\text{sel}_{f,a}$ & selectivity of fleet $f$ at age $a$ for SPR-based reference points\\
$\overline{F}_{f,a}$ & Average fishing mortality for fleet $f$ at age $a$ over user-specified set of years\\
$\upphi(\widetilde{F})$ & equilibrium spawning biomass per recruit for stock $s$ at fully-selected fishing mortality rate $\widetilde{F}$\\
$\widetilde{\mathbf{O}}_{a,r_s,\cdot}$ & proportion surviving the year at age $a$ and occuring in each region (columns) given alive on January 1 in region $r_s$\\
$\mathbf{O}_{a,\cdot,r_s}(t_s)$ & proportion surviving the year at age $a$ starting in each regin (rows) and occuring in region $r_s$ at spawning time $t_s$\\
$\widetilde{\nu}({\widetilde{F}})$ & matrix of equilibrium yield per recruit by region and fleet at fully-selected fishing mortality rate $\widetilde{F}$\\
$\lambda_s$ & weight for stock $s$ to use for spawning biomass per recruit for defining SPR-based fishing mortality reference point
